Fundamentals of Computing and Data Display

### 2019-12-06 Paper/paper-draft-Padgett-Thiam.Rmd
hide api keys

Below is our token to access the Twitter API and start collecting tweets.

```{r, eval=FALSE}
create_token(
  app = "fcdd-course",
  consumer_key = "7y8Xu96DRkBoLsdP8XbQJXTn9",
  consumer_secret = "MCM7gcAfTJKwHks2yIRZaDZcODRQCJBusiYoZtobj4XvO7bvpV",
  access_token = "967157671353864192-DvdUZcJN1ocpqx74YN2GwyejeIMR1Da",
  access_secret = "KkCoMdH1vuivbWgH6IdDaDuiScNcxr389caRbhG2L2kXW"
)
```

>>>>

Below is our token to access the Twitter API and start collecting tweets. Note that these codes are fake, for security purposes.

```{r, eval=FALSE}
create_token(
  app = "fcdd-course",
  consumer_key = "XXXXXXXXXXXXXXXXXXX",
  consumer_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX",
  access_token = "XXXXXXXXXXXXXXXXXXX-XXXXXXXXXXXXXXXXXXX",
  access_secret = "XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX"
)
```
